DS Tuc b is Aligned?

### 2019-10-16 paper/main.tex

Planets in young clusters are valuable resources to provide cleaner test cases. Dynamical interactions like the Kozai-Lidov effect can, depending on the system architecture, occur over hundreds of millions or billions of years \citep{Montet15c, Naoz16}. 
For systems with younger ages, we can rule out certain dynamical interactions, meaning it is likely that the orbit of the planet traces the orbit of the now-dissipated disk.

The orientations of protoplanetary disks relative to the spin of their host stars provide information about the formation of hot Neptunes and hot Jupiters.
The origins of hot Jupiters are still unclear \citep{Dawson18}.
Kozai-Lidov cycles and tidal friction are often invoked to explain the formation of hot Jupiters \citep{Fabrycky07}, but smooth disk migration provides a reasonable alternative in many cases \citep{Ida08}. 
It is possible that multiple channels are required in order to explain all of the observed systems: \citet{Nelson17} analyze data from the HAT and WASP exoplanet surveys and find the data can be well-fit by a model in which $\sim85\%$ of hot Jupiters are formed through high-eccentricity migration and $\sim15\%$ through disk migration.

Disk migration

We don't know how big young things get there? Are they scattered in or is the disk torqued by a massive binary companion like Connie suggests might happen?

>>>>

The origins of hot Jupiters are still unclear \citep{Dawson18}.
Kozai-Lidov cycles and tidal friction are often invoked to explain the formation of hot Jupiters \citep{Fabrycky07}, but smooth disk migration provides a reasonable alternative in many cases \citep{Ida08}. 
It is possible that multiple channels are required in order to explain all of the observed systems: \citet{Nelson17} analyze data from the HAT and WASP exoplanet surveys and find the data can be well-fit by a model in which $\sim85\%$ of hot Jupiters are formed through high-eccentricity migration and $\sim15\%$ through disk migration.

Planets in young clusters are valuable resources to provide clean test cases for planet formation. 
Dynamical interactions like the Kozai-Lidov effect can, depending on the system architecture, occur over hundreds of millions or billions of years \citep{Montet15c, Naoz16}. 
For systems with younger ages, we can rule out certain dynamical interactions, meaning it is likely that the orbit of the planet traces the orbit of the now-dissipated disk.

Therefore, by measuring the obliquity of the orbits of young planets relative to the spin of their host stars, we are tracing the obliquity of their disks. 
Observing a population of these systems will allow us to understand statistical disk properties. 
Alignment of planetary systems and their host stars is often taken as evidence in favor of smooth migration processes. \btmtodo{cite papers here}. 
However, \btmtodo{Batygin citation} suggest wide binary companions or nearby stars in the birth cluster can torque disks to random inclinations over the lifetime of the disk. With a statistical sample of the obliquities of young planets, we can test this hypothesis.

Such a survey is limited by the small number of planetary systems around young stars. There are only a handful of planets known to be younger than 100 Myr, identified by their membership in young moving groups or star forming regions \btmtodo{citep David19, Mann, others}.

Recently, data from the Transiting Exoplanet Survey Satellite \citep{Ricker14} were used to identify a planet around the star DS Tuc A \citep{Bennatti19, Newton19}. 
DS Tuc is a member of the Tucana-Horologium (Tuc-Hor) assocation
